\chapter{Dictionary\label{cha:dict}}

\begin{itemize}
    \item Product: any good whose price is compared at the idealo's website (e.g. White Album from The Beatles).
    \item Category: class. We want to classify products into categories (e.g. Audio-Cds). The names are originally in German, therefore in this work it's translated into English.
    \item Category Tree: structure where categories are situated. Each node and leaf represents each category. A category is a child of other, when semantically one contains the other one (e.g. the category node "Schue" (shoes) is a child of the category node "Mode und Accessoires" (Fashion and Accessories).
    \item Super Category: category belonging to the first level of categories, in the category tree.
    \item Node Category: category that have at least one category child
    \item Leaf Category: category that doesn't have any child.
    \item Target Category: category that represent any product (i.e. there is at least one product, whose assigned category is the target category). Naturally, there are categories that aren't assigned to any product (always node categories).
    \item X-Level Category: category belonging to the level X of the category tree. Super Categories are First-Level categories. The deepest level is level 6. The root is level 0.
    \item Predicted Category: predicted class.
    \item Real Category: real class of a product
    \item Predicted Super Category: predicted first layer class.
\end{itemize}

TODO: Symbols dictionary

